Hydra Battles and Cie

### 2021-06-04 doc/part-hydras.tex
update on Omega link
fix link On_plus in pdf

\vspace{4pt}
\noindent\emph{From Library~\href{../theories/html/hydras.OrdinalNotations/ON_Omega.html}{OrdinalNotations.ON\_Omega}}

@@

\vspace{4pt}
\noindent\emph{From Library~\href{../theories/html/hydras.OrdinalNotations/ON_plus.html}{OrdinalNotations.ON\_plus}}

>>>>

\vspace{4pt}
\noindent\emph{From Library~\href{../theories/html/hydras.OrdinalNotations.ON_Omega.html}{OrdinalNotations.ON\_Omega}}

@@

\vspace{4pt}
\noindent\emph{From Library~\href{../theories/html/hydras.OrdinalNotations.ON_plus.html}{OrdinalNotations.ON\_plus}}
